Title

### 2023-06-13 main.tex
Cambios

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}
%Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

@@

\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}

@@

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which are described by the theory of quantum
channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
manera mas natural. Quizá mas adelante}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
\cpnote{Aca citar nuestros trabajos con Davalos. }
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
ver a Tomas y luego reescribirlo yo}

\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
Additionally, we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them. 
\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
integrando e hilando las ideas. Si hay preguntas, me dices que tos.}

The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
for implementing a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to determine the operations that can be 
performed using a parametrized circuit 
with only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation\cpnote{no entiendo esta frase}. 
Therefore, the results of the last section imply that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

For the particular case of one qubit, we can show some examples of Pauli
dynamical maps implementable with a 1PR circuit, which are plotted in
\fref{fig:curves1}.

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
this curve of states is \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.}
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. }
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits is:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

@@

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\end{itemize}

@@

% }}}
\section{Conclusion} % {{{
\tbnote{Primera versión para ir teniendo algo escrito }\\

In this study, we focused on the analysis of Pauli channels in $N$-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.

\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
muy buena primera iteracion para las conclusiones!!! }
% }}}

@@

%\bibitem{bib3}
%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
%  infection through a transposon insertion followed by a {D}uplication}.
%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
%
%\end{thebibliography}
\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
\textbf{References}
\bibliography{Bibliography}

>>>>

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Pauli channels are fundamental in the context of quantum computing as they model noise in quantum devices. 
We propose a quantum algorithm for simulating Pauli channels on quantum computers 
and extend it to encompass Pauli dynamical maps 
(parametrized Pauli channels).
A parametrized quantum circuit is employed to accommodate for dynamical maps. 
We also establish the mathematical conditions for an
N-qubit transformation to be achievable using a parametrized circuit where
only one single-qubit operation depends on the parameter. 
The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
for the case of one qubit, and the fidelity of this implementation is obtained.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
%\section*{Author summary}

@@

\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}
\tbnote{Va, ya puse un abstract basado en lo que vi en articulos de PlosOne}
\tbnote{Para el título, tengo las siguientes propuestas:}
{\color{green}
\begin{itemize}
\item Quantum Algorithm for Simulation of Parametrized Pauli Channels.
\item Parametrized Pauli Channels Simulation in Quantum Computes.
\item Quantum Simulation of Pauli Channels: Algorithm, Implementation and 
generalization to parametrized channels.
\end{itemize}
}

@@

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which can be described by the theory of quantum
channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{red} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
manera mas natural. Quizá mas adelante}
\tbnote{Va, es cierto.
Puedo incluir más trabajos y hablarlo más en general para que no se sienta forzado:}
{\color{purple}
Such systems have been simulated because of their many applications, 
such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
studying dissipative processes~\cite{Barreiro}
and modeling non-Markovian dynamics~\cite{Marsden}.
}

Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Davalos,Zbigniew,geometry}, 
\cpnote{Aca citar nuestros trabajos con Davalos. } \tbnote{Ya agregué la cita}
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
ver a Tomas y luego reescribirlo yo}
\tbnote{Va, sí lo veo, gracias!}

\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
\tbnote{Lo de Barreiro es una de las citas que agregué nuevas arriba}
\tbnote{Para lo de lo abrupto, quizá una frase como:} 
{\color{purple} To represent the algorithms
done in quantum computers, either
to simulate a physical system or for some other purpose,
one often uses a quantum circuit~\cite{chuangbook}.}
In this work, we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them. 
\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
\tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}

{\color{purple}  
In this article,
after providing the definition of quantum
channels and $N$-qubit Pauli channels
in section \ref{sec: Pauli Channels},
 our first objective is to present a 
quantum algorithm capable of simulating Pauli channels on quantum computers.
We do this in section \ref{sec: Circuit for a Pauli Channel},
where we also demonstrate its implementation using IBM's quantum computers for 
the particular case of single-qubit Pauli channels.

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
Therefore, in section \ref{sec: 1PR Circuits}
we shift our focus to study parametrized
quantum channels, 
aiming to
adapt the algorithm developed for channels 
to dynamical maps. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which  sets the mathematical conditions for the transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map},
we conclude about the 
Pauli dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
}

\tbnote{Y esto ya se va entonces}
{\color{red}
The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
for implementing a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to determine the operations that can be 
performed using a parametrized circuit 
with only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.}

@@

We can now use the previous results to conclude directly which Pauli dynamical maps
can be implemented with a 1PR circuit.
{\color{red} Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
to implement the map
has to be constructed with only one parametrized rotation.}
\cpnote{no entiendo esta frase} 
\tbnote{Si, no está bien escrita. Cambiar por:}
{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
has to be constructed with only one parametrized rotation,
so it has to satisfy the conditions of theorem \ref{theorem2}.
}
Therefore, this implies that the the map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\label{eq:vec}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
\end{eqnarray}
where $|a\rangle,|b\rangle,|c\rangle$ fulfill
the conditions of \eref{eq:conditions-vecs}.

For the particular case of one qubit, we can show some examples of Pauli
dynamical maps implementable with a 1PR circuit, which are plotted in
\fref{fig:curves1}. 
{\color{purple} The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
However, we also include a more uncommon map, which we call the parabolic dynamical map,
defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
This map traces a parabola inside the tetrahedron connecting two of its vertices
and it describes a frontier in the tetrahedron between Pauli channels
that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
}

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that 
${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
Then, taking the $\beta_j$ to be real,
this curve of states can be \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.} 
\tbnote{Sí es correcto, va}
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
\end{align*}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. } \tbnote{Va, listo, lo puse en morado}
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
\label{eq:parab}
\end{eqnarray}
with $p \in [-1,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits can be:
\begin{eqnarray}
|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
\end{align*}
with $\sin s = p$, so that
this map fulfills the conditions of  \eref{eq:conditions-vecs}.

@@

Furthermore, we can construct other examples of 
Pauli dynamical maps such that they
can be implemented with a 1PR circuit.
To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
that satisfy the conditions of  \eref{eq:conditions-vecs}.
For example, this can be done systematically for the case of curves of states of two qubits
(that is, for Pauli dynamical maps of one qubit)
with the following procedure:
\begin{itemize}
\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
This can be done by selecting two angles
$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
\begin{align*}
|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
\end{align*}
\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
los detalles. }
\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
\tbnote{No, no lo hago con CUE ni nada así por lo de que el
primer renglon debe de tner una forma particular y no sabría cómo agregar eso tras
elegir una matriz de CUE.}
\tbnote{Lo que hago es empezar con ese renglon y busco un segundo renglón que sea ortogonal al primero y normalizado.
Para ello, tomo tres vectores $w_1, w_2, w_3$
normalizados y ortogonales al primer renglon.
Entonces, el segundo renglon será en general
de la forma $r_1 w_1 + r_2 w_2 + r_3 w_3$
con $r_i$ complejos y que $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ (para que el 
segundo renglon esté normalizado).
Entonces, busco esos $r_1, r_2, r_3$ al azar  
(básicamente las partes reales e imaginarias
de las $r_i$ deben de estar en una 6-esfera,
por lo que escojo un punto al azar en dicha esfera).}

and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
This way, given that the primed states are orthogonal and their squared norms add up to one,
so do the unprimed states and therefore 
fulfill the conditions of  \eref{eq:conditions-vecs}.

@@

To fulfill this additional condition,  we restrict the first row of
$V$ written as a matrix in 
the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
That way, 
\begin{align*}
|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
\end{align*}
The last equality comes from the fact
that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
$e^{i\theta}$. 
Furthermore, the other entries have to be $0$,
since otherwise the norm of the result would be greater than
$1$ but $V$ is unitary and therefore preserves the norm.
\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
acomode bien a lo que ambos nos parezca.}
\tbnote{Jaja sí, va}
\end{itemize}

@@

% }}}

\section{Conclusion} % {{{
\tbnote{Primera versión para ir teniendo algo escrito }\\

In this work, we focused on the analysis of Pauli channels in $N$-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.
{\color{purple}
Consequently, this work presents another example of the
simulation of open quantum systems, and their
implementation in a quantum computer. }

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.
{\color{purple} Therefore, it can be useful for simplifying any algorithm
that requires a parametrized quantum circuit,
such as those for quantum machine learning.}

\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
muy buena primera iteracion para las conclusiones!! }
\tbnote{Ah, supongo que lo de volver a expandir y hablar en general para terminar de hacer la forma de ``hourglass''
en el artículo. Agregué algo en morado para eso.}

% }}}

@@

%\bibitem{bib3}
%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
%  infection through a transposon insertion followed by a {D}uplication}.
%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
%
%\end{thebibliography}
\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
\bibliography{Bibliography}
